\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Use consistent capitalization for Tor Launcher

\section{Conclusion} 
\label{sec:conclusion}
We measured why and how users have a hard time connecting to Tor through this usability evaluation of Tor launcher. We believe that this is because the interface requires users to know technical terms, provides a lot of freedom for error, and does not give proper feedback. Users in heavily censored environments will likely not succeed in connecting to Tor without outside help. We encourage more usability studies on security tools in general as well as other Tor applications, as they have the potential to create user growth, help user retention, and prevent user frustration. Tor Browser version~5.4.5 incorporated  changes based on our work. We also talked with Tor developers about automating connections to Tor, and they are now considering this as future work.

\section {Acknowledgments}
We would like to thank the peer reviewers, especially our shepherd Jens Grossklags, for giving us valuable feedback on this paper. Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints. This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (Secure Computing Research for Users' Benefit)~\cite{scrub}, and BLUES (Berkeley Laboratory for Usable and Experimental Security)~\cite{blues} laboratories, with support from
Intel, the National Science Foundation,
the Open Technology Fund through the Freedom2Connect Foundation, and from
the US Department of State, Bureau of Democracy, Human Rights and Labor.

>>>>

\section{Conclusion} 
\label{sec:conclusion}
We measured why and how users have a hard time connecting to Tor through this usability evaluation of Tor Launcher. We believe that this is because the interface requires users to know technical terms, provides a lot of freedom for error, and does not give proper feedback. Users in heavily censored environments will likely not succeed in connecting to Tor without outside help. We encourage more usability studies on security tools in general as well as other Tor applications, as they have the potential to create user growth, help user retention, and prevent user frustration. Tor Browser version~5.4.5 incorporated  changes based on our work. We also talked with Tor developers about automating connections to Tor, and they are now considering this as future work.

\section {Acknowledgments}
We would like to thank the peer reviewers, especially our shepherd Jens Grossklags, for giving us valuable feedback on this paper. Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor Launcher and internal constraints. This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (Secure Computing Research for Users' Benefit)~\cite{scrub}, and BLUES (Berkeley Laboratory for Usable and Experimental Security)~\cite{blues} laboratories, with support from
Intel, the National Science Foundation,
the Open Technology Fund through the Freedom2Connect Foundation, and from
the US Department of State, Bureau of Democracy, Human Rights and Labor.
